Polar FarmBot is a CNC robot that will automate the agricultural growing process. It will be able to plant seeds, water plants, measure soil conditions, and remove weeds. The system will not be able to harvest plants nor remove pests from the plants. It will be stationed in a backyard and will be used to grow various fruits and vegetables such as carrots, lettuce, watermelon, onions, and much more along with all kinds of spices and herbs.

Polar FarmBot will have a central pole in which an arm pivots around. The arm will extend outward from the central pole at variable lengths depending on the size specified by the consumer. At the end of the arm there will be a support that extends downward to a set of wheels that allow the arm to move in a circular direction around the central pole. Along the arm there will be a gantry system that will be powered by a motor to move horizontally back and forward on the arm. The gantry will also have a separate motor that will power a separate arm that moves up and down in the vertical direction. Attached to the rod will be the seeder, water pump, and soil monitor tool assembly. Cables and connectors will be routed through the arm, down the central pole, and back out to a control box located just outside the gardening plot. Within the control box, there will be a motor driver and raspberry pi. The motor driver will power all the motors and sensors on the gantry. The raspberry pi will connect to the internet that will allow for a web based user interface to interact with the system. The control box will also house a power supply that will power all the motors, sensors, motor driver, and raspberry pi. There will also be connectors for the vacuum for picking up seeds and also a connector for water that will allow the robot the ability to water plants.

The robot will also connect back to a computer that will have a web interface for users to interact with the robot. From this interface a user will be able to layout a plot, monitor overall plant growth and soil conditions, and see whether or not the plants are ready for harvesting. To go along with the web interface, there will be a companion application developed for android. This app will have all the same functionality as the web app just on a mobile platform. Polar FarmBot will have multiple cameras attached to it to allow monitoring progress remotely.