Cost Proposal: We have default 800 budget provided by UT Arlington department sponsorship funds.  Since, our team do not have any company sponsors for the project, we are currently seeking donations from different companies. Once we gather all the parts from donations, we will buy the remaining parts that we need with our default budget.

Preliminary Budget: The basic categories of components for our Farmbot project are Extrusions, Plates, Fasteners and Hardware, Drivetrain, Electronics and Wiring, Tubing, 3D Prints and Miscellaneous. Our team has estimated to spend about \$100 on Drivetrain, \$200 on Electronics and around \$200 on Miscellaneous since it will include the frame we build the robot in. Here, Extrusions are taken care of through the lab . Fasteners and Hardware and Tubing are covered with the donations from two companies namely Danco and Partsmaster. We are going to use our teammate Arun's 3D printer. We are going to 3D print all the required plates for our project.

Current \& Pending Support: So far, with the great work from our team mate Travis, two companies namely Danco and Partsmaster have already made donations of the following items for our projects:


a> 25' Extension Cord

b> 50' of 18 \& 20 Gauge wire

c> Clamps

d> 25' 1/4" inner diameter tubing

e> 4 sets of 1/4" Barbs

f> Cable ties

g> Electrical Tape

h> Wire Strippers

i> Soldering Iron

j> Solder

k> Wet/dry vacuum

l> All the screws we need

m> 16 motion computing le 1600 computers


Also, our team mate Arun has provided us with 3D printers, 1700 mm of aluminium rod and 20mm*20mm t-slot rail.
