This section describes our intentions for documentation upkeep and expected deliverables for the duration of the project.

\subsection{Project Charter}
This project charter will detail the target goals desired by the team working to it's completion.

\subsection{Product Backlog}
The product backlog is to maintain a list of what work the team will need to deliver for a fully functional product. We will maintain a product backlog on a Team Foundation Server instance hosted on Visual Studio Online. The backlog will be ordered by the product owner from what is considered most important at the top of the backlog to what is considered least important at the bottom of the backlog.

\subsection{Sprint Planning}
We intend to hold sprint planning sessions after our regularly planned meetings. Team members will propose task, features, and other work for upcoming sprints during these sessions. If a majority of the team agrees to commit to completing a work item, it will be estimated for difficulty and entered into the upcoming sprint.

\subsubsection{Sprint Goal}
The sprint goal will be decided by a team vote. 

\subsubsection{Sprint Backlog}
The sprint backlog will be decided by the product owner. The product owner will select the most important items from the top of the product backlog.

\subsubsection{Task Breakdown}
Tasks will assigned to team members who volunteer for them. Remaining tasks will be assigned by 

\subsection{Sprint Burndown Charts}
A sprint burndown chart will be generated by the Scrum Master at the end of every sprint cycle. 

\subsection{Sprint Retrospective}
A sprint retrospective will be held at the first team meeting after the ending of each sprint. 

\subsection{Individual Status Reports}
Individual status reports will be made during the regularly held team meetings. Any exceptionally important information should be posted to the team text communications channels.

\subsection{Engineering Notebooks}
The team members will maintain individual engineering notebooks which will be peer reviewed and signed by other members of the team.

\subsection{Closeout Materials}
At the conclusion of this project we will deliver a functional prototype with a documented assembly guide to replicate the project and all software needed to operate the prototype. This software will be delivered with instructional guides to help with installation. 

\subsubsection{System Prototype}
The system will be prototyped in two stages. The first phase is a pure hardware design phase, during which a small scale unit will be constructed.This small scale unit will be used to develop control firmware and finalize the design of the primary components, but will be constructed in limited space. During the second development stage a second prototype will be created which will utilize all the mechanical designs developed during the first stage, but without space limitations. 

\subsubsection{Project Poster}
We will design and produce a poster to help explain the problem we are trying to address, the solution we are proposing, differences between our project and the FarmBot project, and finally demonstrate our design solution.

\subsubsection{Web Page}
We will make a simple interactive web page which will demonstrate the project and link to further documentation. The web page will also credit all our sponsors.

\subsubsection{Demo Video}
A full system operation video will be made a link to that video will be available on the product web page.

\subsubsection{Source Code}
The source code for the project will be made available on a public git based repo.

\subsubsection{Source Code Documentation}
The source code will be documented with Doxygen and made available with the source code.

\subsubsection{Hardware Schematics}
Hardware scematics will be posted with the source code.

\subsubsection{CAD files}
CAD files will be made with OpenSCAD and will be part of the source code.

\subsubsection{Installation Scripts}
The project deliverables which are designed to be deployed by users will have installation scripts. Documentation will be delivered with the instillation scripts to guide users through their use.

\subsubsection{User Manual}
The user manual will be created on a wiki style site. This will allow maintenance by dedicated users after the project is delivered.