Arun Kalahasti will lead hardware development, act as Scrum Master for the team, and aid in software design and implementation. As Scrum Master he will be expected to maintain documentation and establish sprint goals. Arun has the most experience in the team with hardware development and implementation, therefore his responibilities as lead harware developer will be to establish and maintain project hardware and physical design. He also has experience with creating systems in many development platforms, incuding Android, Java, C++, C\#, .NET, Javascript, several Javascript frameworks, Arduino, Python, and will therefore contribute to software design and implementation.

Travis Matthews will lead Software Development and aid in hardware design and implementation. Working with Arduino projects and building various electrical circuits, Travis will be able to contribute well to the the hardware design process. Travis also has extensive experience in software development; creating systems in Android, iOS, ASP.NET, Java, C++, C\#, and Python. He will be in charge of building the wireframes for the software systems and come up with how the systems will interface with each other other. Along with managing the software systems, Travis will also be a developer in creating these systems.

Saman Shrestha would work as a general developer. Having a background in computer science he would be better writing codes for the software of the FarmBot. He has worked on various coding platforms and is good in Java, C and python. He would also help in building the bot. He is really interested on the hardware aspect of the project and would help putting the bot together.

Santosh Pradhan will assist in Software Development and also in hardware design and implementation. He has an experience working in java, c, python and database. He will also contribute in building electrical circuits and assembling different hardware parts. Also, he will be researching and helping out to design an efficient and economical robot. 

Bipin Ghimire will help building the software and harware of the project and also assist in research of the project.
